---
title       : App to predict MPG of a car
subtitle    : Linear model to predict MPG of a car to help car buyers
author      : YVH
job         : Presenter
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, shiny, interactive, bootstrap, quiz]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Problem introduction 

- People want to buy a car that has high Miles Per Gallon (MPG)
- But ... 
- What is affecting MPG the most?
- Transmission? Weight? 
- Different standards of measurements give different MPG, they cannot be compared easily
- This app give you a general idea of what to look for 


--- .class #id 

## Data and linear model

- This app uses the mtcars dataset that comes with R 
- A study has been performed to find the parameters that influence MPG the most
- A linear fit was performed in following way:
```{r, eval=FALSE}
  fit <- lm(mpg ~ factor(am) + factor(cyl) + wt, data = mtcars)
```
- Out of studying a lot of fits the number of cylinders and the weight of the car are the most determining factors for MPG 
- This fit is the core of the developped shiny app.


--- .class #id 

## Shiny app 
- https://yvestools.shinyapps.io/Shiny_app_yv/
- Preview of app:
```{r, opts.label = 'shiny'}
slidifyUI(
#  headerPanel("Predict MPG of a car using the mtcars dataset"),
  sidebarPanel(
    selectInput('am','Transmission',choices = list("Automatic"=0,"Manual"=1),
                selected = 0),
    sliderInput('cyl', 'Number of cylinders',value = 2, min = 4, max = 8, step = 2),
    sliderInput('wt', 'Weight of the car [10^3 lb]', 0.1, min = 0.1, max = 5.5, step = 0.01),
    submitButton('Submit')
  ),
  mainPanel(
   )

)
```
- Fill in values and press submit and the app will predict the MPG. 



--- .class #id 

## Example of usefulness
- Suppose you want to buy a car with high MPG. 
- You have the choice between car #1 (2000 lb) with 6 cylinders and automatic transmission and car #2 with manual transmission, 8 cylinders and a mass of 2100 lb.
- Using the app: MPG car #1 has MPG of 23.20 and MPG car #2 is 21.20
- You drive 310 miles per week or 16120 miles per year
- Car 1: 695 Gallons/year; car 2: 760 Gallons/year
- Prize of a gallon is about USD 2
```{r }
  c(695*2,760*2,(760-695)*2)
```
- Cost of fuel car 1: USD 1390 and car 2: USD 1520 per year 
- Car 1 saves you $130/year in fuel  






